\textsc{\wobble: a data-driven method for precision radial velocities}

### 2018-12-20 paper/paper.tex
minor edits, two-column
Former-commit-id: fb302b07e950c4aefd8076a9a750ce27f1d8575a

The resulting \RV signal retrieved by \wobble is shown in Figure \ref{fig:hd189_rm}. 
We fit the signal using \starry \citep{Luger2018}, which computes analytic occultation
light curves for bodies whose surfaces can be decomposed into sums
of spherical harmonics. Since the radial component of the velocity field of a 
differentially rotating star can be expressed in terms of polynomials in 
$x = \sin\theta\cos\phi$, $y = \sin\theta\sin\phi$, and $z=\cos\theta$, where
$\theta$ is the polar angle and $\phi$ is the azimuthal angle \citep[c.f. Equation 91 in][]{Short2018},
this velocity field may be expressed exactly in terms of spherical harmonics
\citep{LugerBedell2019}.
We therefore use \starry to fit for the equatorial rotational velocity, the inclination,
the obliquity, and the shear due to differential rotation of the star, closely
following the analysis performed in \citep{Cegla2016}.
We infer a projected stellar obliquity $\lambda = -0.43 \pm 0.34^\circ$, in close agreement
with the value reported in \citet{Cegla2016}. Our inferred values for the other parameters
are broadly consistent with the results in \citet{Cegla2016}, except with significantly
higher uncertainty due to the fact that we are unable to constrain the stellar inclination
due to the $v\sin i$ degeneracy. We attribute the narrower posteriors in \citet{Cegla2016}
as a difference in the choice of prior.
\footnote{See \href{https://github.com/megbedell/wobble/tree/master/scripts/DifferentialRotationWithSphericalHarmonics.ipynb}{this interactive notebook} 
          for a derivation of the spherical harmonic decomposition of the stellar velocity field. 
          The notebook used to perform our analysis and produce Figure~\ref{fig:hd189_rm} can be found 
          \href{https://github.com/megbedell/wobble/tree/master/scripts/HD189733bWithStarry.ipynb}{here}.}

@@

Even working within \wobble's current assumptions and running on \HARPS data, there are potential changes to be made to the implementation of \wobble that may improve its performance. 
Many of these are quite basic and straightforward changes to be made within the existing framework of \wobble. 
We discuss some of potential adjustments here.

Perhaps the most obvious shortcoming of \wobble is its reliance on regularization. 
We chose this framework because it keeps the model convex and its implicit assumptions (that the spectra are a flat continuum by default) closely mirror our physical understanding. 
However, setting the regularization amplitudes optimally is by far the computationally slowest and most unwieldy part of applying \wobble to a new data set. 
In principle, as data sets get larger, regularization becomes less necessary. 
One way to remove the need for telluric regularization might be to run on a data set that is composed of many different stars, each with their own individual spectra and \RVs but with a shared telluric component, so that the data informing the telluric lines is sufficiently large. 
This could be done with relatively trivial changes to the \wobble code, although it would require strong computational resources.

One choice that \wobble makes differently from other data-driven \RV codes is the way we represent the underlying spectral components. 
We use an extremely simple representation: a model grid of wavelengths and corresponding fluxes that gets linearly interpolated by the $P$ operator. 
One possible improvement would be to go to a higher-order interpolation scheme. 
Another approach would be a non-parameteric method like a Gaussian process \citep[as in][]{Czekala2017}. 
A third approach would be to use a model that incorporates more physics: this could range from a model with fixed lines that may vary only in terms of common line profile parameters to a complex model including various atomic and molecular physics of the lines. 
A sensible way to implement this within the existing \wobble framework might be to add a physically motivated mean spectral template and optimize $y_{\star, n}$ vectors of residuals away from this template. 
In any case, the general approach of \wobble does not depend intrinsically on the spectral representation, and swapping out the current representation for something else is simple, provided that the representative function can be implemented in \TF.

>>>>

The resulting \RV signal retrieved by \wobble is shown in Figure \ref{fig:hd189_rm}. 
We fit the signal using \starry \citep{Luger2018}, which computes analytic occultation
light curves for bodies whose surfaces can be decomposed into sums
of spherical harmonics. Since the radial component of the velocity field of a 
differentially rotating star can be expressed in terms of polynomials in 
$x = \sin\theta\cos\phi$, $y = \sin\theta\sin\phi$, and $z=\cos\theta$, where
$\theta$ is the polar angle and $\phi$ is the azimuthal angle \citep[c.f. Equation 91 in][]{Short2018},
this velocity field may be expressed exactly in terms of spherical harmonics
\citep{LugerBedell2019}.
We therefore use \starry to fit for the equatorial rotational velocity, the inclination,
the obliquity, and the shear due to differential rotation of the star, closely
following the analysis performed in \citet{Cegla2016}.
We infer a projected stellar obliquity $\lambda = -0.43 \pm 0.34^\circ$, in close agreement
with the value reported in \citet{Cegla2016}. Our inferred values for the other parameters
are broadly consistent with the results in \citet{Cegla2016}, except with significantly
higher uncertainty due to the fact that we are unable to constrain the stellar inclination
due to the $v\sin i$ degeneracy. We attribute the narrower posteriors in \citet{Cegla2016}
to a difference in the choice of prior.
\footnote{See \href{https://github.com/megbedell/wobble/tree/master/scripts/DifferentialRotationWithSphericalHarmonics.ipynb}{this interactive notebook} 
          for a derivation of the spherical harmonic decomposition of the stellar velocity field. 
          The notebook used to perform our analysis and produce Figure~\ref{fig:hd189_rm} can be found 
          \href{https://github.com/megbedell/wobble/tree/master/scripts/HD189733bWithStarry.ipynb}{here}.}

@@

Even working within \wobble's current assumptions and running on \HARPS-like data, there are potential changes to be made to the implementation of \wobble that may improve its performance. 
Many of these are quite basic and straightforward changes to be made within the existing framework of \wobble. 
We discuss some potential adjustments here.

Perhaps the most obvious shortcoming of \wobble is its reliance on regularization. 
We chose this framework because it keeps the model convex and its implicit assumptions (that the spectra are a flat continuum by default) closely mirror our physical understanding. 
However, setting the regularization amplitudes optimally is by far the computationally slowest and most unwieldy part of applying \wobble to a new data set. 
Dealing with the possibility of overfitting is an inevitable requirement of any model, especially one that relies on as many free parameters as \wobble. 
That being said, in principle as data sets get larger, regularization becomes less crucial. 
One way to lessen the need for telluric regularization might be to run on a data set that is composed of many different stars, each with their own individual spectra and \RVs but with a shared telluric component, so that the data informing the telluric lines is sufficiently large. 
This could be done with relatively trivial changes to the \wobble code, although it would require considerable computational resources.

One choice that \wobble makes differently from other data-driven \RV codes is the way we represent the underlying spectral components. 
We use an extremely simple representation: a model grid of wavelengths and corresponding fluxes that gets linearly interpolated. 
One possible improvement would be to go to a higher-order interpolation scheme. 
Another approach would be a non-parameteric method like a Gaussian process \citep[as in][]{Czekala2017}. 
A third approach would be to use a model that incorporates more physics: this could range from a model with fixed lines that may vary only in terms of common line profile parameters to a complex model including various atomic and molecular physics of the lines. 
A sensible way to implement this within the existing \wobble framework might be to add a physically motivated mean spectral template and optimize $y_{\star, n}$ vectors of residuals away from this template. 
In any case, the general approach of \wobble does not depend intrinsically on the spectral representation, and swapping out the current representation for something else is simple, provided that the representative function can be implemented in \TF.
